---
title: "Module 2 New Jersey Policing"
author: "Tristan Tran and Ian Nel"
date: "`r Sys.Date()`"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
source('src/preprocess_data.R')
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).
## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  "src/ftp",
  options = list(
    width = "100%", height = 550
  )
)
```

This app features two inputs that allow the user to select the type of force they would like to query for the visual. This checkbox input will select which types of forxe will be used where we will display the change between the period between 2012-2016 and 2020-2021.

The drop down list allows the user to select which departments which to visualize. The summary tabs and officers tabs allow 



